### 2019-11-28 thesis.tex
Made corrections until page 27. Next correction is in page 23

With the lowest order of this chain of perturbative approximations, the
linear theory, it is possible to obtain the dispersion relations, which
are mathematical expressions that not only help us on identifying the
different oscillatory modes that may be excited in plasmas, but also
wholly characterizes these oscillations. Valuable information like
how these waves propagate and the frequencies that will resonate with
the plasma particles, resulting in damping or amplification of these
oscillations \cite{bitt,chen,gurnett2017}, are given by the dispersion
relations. This information, however, is static. There is no way to
know, based solely on the linear formulation, any further development
of the system, how these waves will evolve in time from a given initial
state, for instance. Thus, to clarify if these oscillations will grow
until their amplitudes become too large to be treated by a perturbative
method, or if they will rapidly increase and saturate, or if they will
be completely damped, or if they will decrease a little and then saturate, 
a certain degree of nonlinearity must be taken into account. That is the
purpose of the quasilinear approximation.

In the quasilinear theory, low-order nonlinear terms are kept in
the equation for the time evolution of the velocity distribution
function. The velocity distribution will then evolve in time through
a process of diffusion in velocity space, in which the diffusion
coefficient depends on the spectral energy density of the waves.
The dispersion relation is formally given by the same expression
obtained under the linear theory, except that now it depends on a
time-dependent velocity distribution function, which must vary in a
much slower time-scale than the period of the plasma oscillations.
Under such condition, the gradual changing on the velocity space
shape slowly modifies the shape of the wave spectrum, whose new form
will alter the velocity distribution function and so on, until a new
quasi-stationary equilibrium state is attained \cite{gurnett2017}.
However, depending on the phenomenon being described this saturation
state reached under the quasilinear approximation might keep on evolving
if higher order nonlinearities are taken into account \cite{akhi2}.
This kind of nonlinear analysis is given by the
\emph{weak turbulence theory}, which is the next step in this chain
of perturbative approximations.

Mostly developed in the period between the late $1950$s and early
$1970$s \cite{Kadomtsev1965,Tsytovich1967,saggal,tsynlep,david,
  tsyitotp,akhi2,tsytotp,mel}, the weak turbulence theory has
become a valuable theoretical tool for the analysis of nonlinear
phenomena in plasmas since then, being applied in several studies
until nowadays \cite{Grognard1982,McClements87b,Hanssen1991,
  Edney2001,Kontar2001,Kontar2002,THD13}. Its complex formulation
is constituted by a set of coupled kinetic equations, which describe
the time evolution of the velocity distribution functions of the
plasma particles and the time evolution of the spectral intensities of
the plasma wave modes. The development of the weak turbulence theory
was resumed in a relatively recent series of papers, where the author,
starting from first principles, has extended the original formalism in
order to include new effects. In the initial work, it was considered
only the propagation of electrostatic oscillations, taking into account
the effects of both wave-wave and wave-particle interactions \cite{Yoon00}.
Later, the formalism was expanded, and the effects of discrete particle,
related to spontaneous emission and spontaneous scattering processes
were included \cite{Yoon05a}. In a further extension, the effects of
the propagation of electromagnetic waves were incorporated into the
revised formulation \cite{Yoon06,Yoon2012b}.

@@

The hypothesis about the probable relevance of binary collisions in the
nonlinear dynamics of the beam-plasma interaction was numerically tested
in \cite{Tigik2016a} (see \autoref{master}). In this work, a linearized
form of the Landau collision integral was added into the particle kinetic
equation, and the weak turbulence theory's complete set of self-consistent,
electrostatic equations was numerically integrated in two-dimensions.
It was shown that collisions indeed do affect the plasma dynamics in a
time-scale that is very close to the time-scale of action of nonlinear
effects. Beyond the purely theoretical conjecture, combining collective
processes and collisional effects have some important applications in
solar physics. In the solar hard X-ray emission analysis, for instance, the
models used for interpreting the spectra measured by the Reuven Ramaty High
Energy Solar Spectroscopic Imager (RHESSI)\footnote{For more information
 about the mission see: \url{https://hesperia.gsfc.nasa.gov/rhessi3/}.}
that employ quasilinear/nonlinear wave instabilities with some kind of
collisional dissipation (collisional damping for the waves, binary
collisions for the particles) are usually empirically adapted merely by
adding an \emph{ad hoc} expression into the particles and wave kinetic
equations to fit the observed data \cite{PK95,Kohl1998,Veronig05,Brown2006,
  Kontar2011,KKDSSK11}. However, there is no rigorous theory to compare
and support such models. Moreover, though the formalism in \cite{Tigik2016a}
makes use of the full Landau collision integral in the particle kinetic
equation, it does not take into account collisional damping effects in the
wave equation, which is widely used in these empirical models. The point
is: until that moment, there was not a proper theoretical tool to deal
with the combination of collective processes and collisional interaction.

@@

The theory developed during this graduate research analyses the combined
action of nonlinear kinetic instabilities and collisional processes in
the context of solar physics. To contextualize our work within the solar
plasma research, in \autoref{sec:solar-physics} we present a brief review
of the current research in solar and space physics and the phenomena
related to this work. The corresponding paper is pointed in a footnote.

\subsection{Solar and space physics}
\label{sec:solar-physics}
The domain of solar and space physics is the \emph{heliosphere}, a cavity
in the interstellar medium, created by the constant supersonic flow of solar
plasma that permeates the interplanetary space. This region encloses the
solar system and extends for approximately $140\unit{AU}$\footnote{An AU
  (astronomical unit) is defined as the mean distance between the Sun and
  Earth, $1\unit{AU}\approx 150\times 10^6\unit{km}$.} in the surrounding
galactic space. Its outer limit is the \emph{heliopause}, an interface
zone where the outgoing pressure of the solar plasma balances the incoming
pressure from the interstellar medium. This comet-shaped plasma bubble
\cite{Dialynas2017}, also has an inner boundary, the \emph{termination shock},
which delimits the sphere of absolute influence of the solar plasma. Beyond
the termination shock, at roughly $100\unit{AU}$ from the Sun, extending
out to the heliopause, lies the \emph{heliosheath}. In this region, the
solar wind particles start being subjected to increasing external pressure,
transitioning to a subsonic, turbulent flow that blends and interacts
directly with the matter in the local interstellar medium \cite{NAP13060}.
In \autoref{figE1}, we have a depiction of the regions and boundaries
described above, and the current location of both Voyager missions, that
are already outside the heliosphere, in the interstellar space.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.892\textwidth]{solar_system_env.png}
    \caption{Main boundaries of the heliosphere and the location of both
      Voyager missions.}
      {\footnotesize Credit:}
      \href{https://voyager.jpl.nasa.gov/news/details.php?article_id=112}
      {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
    \label{figE1}
  \end{center}
\end{figure}

The ultimate goal of heliophysics can be summarized as the search for a
better understanding of the solar dynamics and how it affects the Earth,
other planetary bodies, and the interstellar medium. The heliosphere is
a coupled system, where different interacting elements that might look
unrelated at first sight are connected by underlying plasma processes
\cite{NAP13060}. A great example of this interconnection is the relation
between the appearance of sunspots and the occurrence of non-recurrent
geomagnetic storms, which are the most intense space weather disturbances.
Evidence of such relationship started to appear at the end of the $19$th
century. However, the correct hypothesis supporting this correlation
(coronal mass ejections associated with solar flares), which depended
on advances in plasma physics theory, came along only in $1929$
\cite{chapman1929cosmical,Koskinen2011}.

\subsection{The Sun and the near-Earth environment}
\label{sec:sun}
A better comprehension of the Sun and the dynamic space around our planet
goes beyond the pure scientific curiosity. This accessible space physics
laboratory can indeed lead to discoveries that can be applied and extended
to remote cosmic systems. However, the primary reason behind the international
effort (see Figures \ref{nasa} and
\ref{esa}) on understanding the complex physics of the Sun and interplanetary
space is to unlock means of predicting the occurrence and intensity of solar
activity, and anticipate how the near-Earth environment will be affected.
Reliable forecasting of the space weather is essential for protecting
electronic equipment, radio communications, GPS signal and humans in space
from the effects of the interaction between the dense, magnetized plasma of
coronal mass ejections with the geomagnetic field, and also from the
energetic radiation emitted by solar flares\footnote{The emission of hard X-rays
  and type III radio bursts, both generated during solar flares, are addressed in
  \cite{Tigik2016a} (see \autoref{master}).}. Extreme coronal mass ejections
can also cause stronger geomagnetic disturbances that may affect terrestrial
infrastructure such as electric power grids \cite{NAP13060}.
\begin{figure}[hb]
  \begin{center}
    \includegraphics[width=0.892\textwidth]{hso_fleet_chart_april_2019.pdf}
    \caption{NASA's present and future heliophysics system observatory. The number
      between parenthesis under the probe's name is the total number of spacecrafts
      that compose the mission.}
      {\footnotesize Credit:}
      \href{https://science.nasa.gov/heliophysics}
      {\footnotesize NASA}{\footnotesize , accessed at 10/08/2019.}
    \label{nasa}
  \end{center}
\end{figure}
\begin{figure}[ht]
  \begin{center}
    \includegraphics[width=0.892\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
    \caption{ESA's past, present, and future science missions for studying the solar system.}
      {\footnotesize Credit:}
      \href{https://www.esa.int/spaceinimages/Images/2019/02/ESA_s_fleet_of_Solar_System_explorers}
      {\footnotesize ESA}{\footnotesize , accessed at 10/08/2019.}
    \label{esa}
  \end{center}
\end{figure}

\subsection{The solar corona}
\label{sec:corona}
The source of the tenuous magnetized plasma permeating the heliosphere, and
also the origin of solar particles and radiation that may cause disruptive
space weather around Earth, is the outermost layer of the Sun: the solar
corona \cite{Cranmer2017,Klein2017}. The solar corona can be easily recognized
as the bright halo that appears around the hidden Sun during solar eclipses.
\autoref{corona} shows two beautiful photographs of the corona, taken in two
different solar eclipses, August 21 $2017$ and July 2 $2019$. In both pictures,
one can see the moon covering the bright photosphere, allowing us to have a
glimpse of the thin, but ultra-hot coronal plasma.

@@

The main subject of this thesis is discussed in \Cref{noneigenmode}. In
\Cref{sec:inc-non} we show the methodology used in the formulation of this
new generalization and the outcome of its inclusion in the quasilinear
wave equation, and in the particle kinetic equation. \Cref{sec:non-non}
describes the inclusion of the noneigenmode fluctuations in the nonlinear
wave equations and the resulting terms, which are the main concern of
the present analysis. In \Cref{main}, we contextualize the present work
regarding the theory discussed in the previous chapter and present the
results obtained in appended papers. \Cref{cha:final}, summarizes the
results and discuss some remarking conclusions obtained in this analysis.
At the end of this chapter, we also deliberate the perspectives for this
new generalized formalism and its relevance for the next generation of
solar physics research.
% LFZ190822: Suponho que aqui devia ser "... a brief discussion on the
% conclusions obtained and on the perspectives ..." ?
% Sabrina: Melhorou?
% and its relevance for the next generation of solar physics research are
% also deliberated.

In the end, we have four appendices. \Cref{appA} depicts an improved
approximation for the second order susceptibility of the electrostatic
bremsstrahlung for Langmuir waves. In \Cref{appB} we discuss the
similarities of the asymptotic equilibrium state of the Langmuir waves
spectrum, considering a combination of an inverse power-law kappa
distribution and a Maxwellian distribution, in the presence and the
absence of the electrostatic bremsstrahlung effect. The discussion in
\Cref{appB} is related with to article appended in \Cref{appC}, which
is parallel research and is only slightly related to the main subject
of this work. \Cref{master} shows the paper that summarizes the results
of my Master’s dissertation, which may be considered the starting point
of this doctoral research. % \Cref{appE} explores relevant aspects of
% current solar physics research and how they are connected to this work.
% It was written to be more like a light, informative reading, than a
% deep academic digression.

@@

Like non-ionized gases, the statistical description of the plasma dynamics
is given by the Boltzmann equation
\begin{equation}
\frac{\partial f_\alpha({\bf r},{\bf v},t)}{\partial t}
+{\bf v \cdot \nabla_r}f_\alpha({\bf r},{\bf v},t)
 +\frac{{\bf F}}{m_\alpha} {\bf\cdot \nabla_v}f_\alpha({\bf r},{\bf v},t)
=\left(\frac{\partial f_\alpha ({\bf r},{\bf v},t)}{\partial t}\right)_{\rm coll}.
\label{boltz}
\end{equation}

@@

Collisional interactions are the central point of the present thesis. However,
the formalism presented in \Cref{noneigenmode}, departs from the weak turbulence
equations, which are the kinetic description of nonlinear, low-amplitude
instabilities in a collisionless plasma. The contribution of the correlations
between \emph{source} fluctuations, which account for collisional interactions
(see.~\cite{klimon,Tigik2015}), are then retrieved with the inclusion of
noneigenmode contributions in the wave and particle kinetic equations\footnote{
  For instance, in \Cref{sec:inc-non}, it will be shown that including the
  noneigenmode fluctuations in the weak turbulence's formal particle kinetic
  equation leads to an expression that accounts for the collisional interactions
  that appear on the right-hand side of equation~\eqref{boltz}.}. Therefore,
at this point, it will be assumed that collisions can be neglected.

@@

In the general case, the acting force in Eqs. \eqref{boltz} and \eqref{eq:vlasov},
is given by the Lorentz force added by an external force, which, at kinetic scales,
is also of electromagnetic nature. Therefore, in \emph{cgs} units\footnote{The
  use of cgs units will be consistent trough all this work.}, ${\bf F}$ has the
following form
\begin{equation}
  {\bf F}=\sum_{\alpha}q_{\alpha}\left[{\bf E}({\bf r},t)
    +\frac{1}{c}{\bf v \times B}({\bf r},t)\right]
  +{\bf F_{ext}},
  \label{florentz}
\end{equation}
where $q_{\alpha}$ is the charge of the particles of kind $\alpha$, and $c$ is
the speed of light. The quantities ${\bf E}({\bf r},t)$ and ${\bf B}({\bf r},t)$
are, respectively, the electric and magnetic fields, which are described by the
Maxwell equations
\begin{eqnarray}
  \label{max1}
  {\bf \nabla \cdot E}&=& 4\pi\rho\\
  \label{max2}
  {\bf \nabla \cdot B}&=& 0\\
  \label{max3}
    {\bf \nabla \times E}&=& -\frac{1}{c}
   \frac{\partial {\bf B}}{\partial t}\\
  \label{max4}
    {\bf \nabla \times B}&=& \frac{4\pi}{c}{\bf J}
    +\frac{1}{c}\frac{\partial{\bf E}}{\partial t}.
\end{eqnarray}

@@

\chapter{Weak turbulence theory}
\label{cha:weak-turb}
The weak turbulence theory is what we may call a ``borderline approach''
because, despite the fact that it deals with some more intense
instabilities, we must assure that these fluctuations are still inside
the weak turbulence limit, i.e., if the turbulence is weak enough to be
treated by a perturbative method. Such boundary is defined by a comparison
between the averaged kinetic energy of the particles per volume unity
${\cal E}_{kin}=\bar n m<v^2>/2$, and the energy density ${\cal E}_f$, which
is associated with the fluctuations of the perturbative electric field.
Thus, by ``weak turbulence'' we mean
\begin{equation}
  \label{eq:weak}
  {\cal E}_f \ll {\cal E}_{kin},
\end{equation}
that is,
% LFZ180216: Não fica melhor com vírgula depois de "that is"?
% Sabrina: OK
the energy density of the fluctuations must be much smaller
% LFZ180216: Ou simplesmente "much smaller"?
% Sabrina: OK
than the kinetic energy density of the particles. This condition is
related to the slow wave-growing assumption \cite{david}, which is
central for the further development of nonlinear kinetic equations,
as will be discussed further.

@@

\section{Nonlinear kinetic equations}
\label{sec:kin-gen-eq}
Let us consider the propagation of electrostatic oscillations
in a homogeneous, unmagnetized and fully ionized plasma. Thus,
in the absence of collisions, the movement equation is given
by the electrostatic Vlasov equation
\begin{equation}
  \label{vlasov-nl}
  \frac{\partial f_a({\bf r}, {\bf v},t)}{\partial t}
+{\bf v \cdot \nabla}f_a({\bf r}, {\bf v},t)
+\frac{e_a}{m_a}{\bf E}({\bf r},t){\bf \cdot}
\frac{\partial f_a({\bf r},{\bf v},t)}{\partial \bf v}=0,
\end{equation}
where the electric field is given by
\begin{equation}
   {\bf \nabla \cdot E}({\bf r},t)
   =4\pi \hat n \sum_a e_a\int d^3 v f_a({\bf r}, {\bf v},t). 
\end{equation}
In the above equations, $f_a$ is the velocity distribution function,
where the subscript ``$a$'' is the kind of particle: $a=i$ for ions
and $a=e$ for electrons. For an overall neutral plasma, the number
density of
% LFZ180216: Sugestão "the number density of"
% Sabrina: OK
the ions and the electrons is the same, $\hat n = \hat n_e = \hat n_i$.

>>>>

With the lowest order of this chain of perturbative approximations, the
linear theory, it is possible to obtain the dispersion relations, which
are mathematical expressions that not only help us on identifying the
different oscillatory modes that may be excited in plasmas, but also
wholly characterize these oscillations. Valuable information like
how these waves propagate and the frequencies that will resonate with
the plasma particles, resulting in damping or amplification of these
oscillations \cite{bitt,chen,gurnett2017}, are given by the dispersion
relations. This information, however, is static. There is no way to
know, based solely on the linear formulation, any further development
of the system, how these waves will evolve in time from a given initial
state, for instance. Thus, to clarify if these oscillations will grow
until their amplitudes become too large to be treated by a perturbative
method, or if they will rapidly increase and saturate, or if they will
be completely damped, or if they will decrease a little and then saturate, 
a certain degree of nonlinearity must be taken into account. That is the
purpose of the quasilinear approximation.

In the quasilinear theory, low-order nonlinear terms are kept in
the equation for the time evolution of the velocity distribution
function. The velocity distribution will then evolve in time through
a process of diffusion in velocity space, in which the diffusion
coefficient depends on the spectral energy density of the waves.
The dispersion relation is formally given by the same expression
obtained under the linear theory, except that now it depends on a
time-dependent velocity distribution function, which must vary in a
much slower time-scale than the period of the plasma oscillations.
Under such condition, the gradual changing on the velocity space
shape slowly modifies the shape of the wave spectrum, whose new form
will alter the velocity distribution function and so on, until a new
quasi-stationary equilibrium state is attained \cite{gurnett2017}.
However, depending on the phenomenon being described, this saturation
state reached under the quasilinear approximation might keep on evolving
if higher order nonlinearities are taken into account \cite{akhi2}.
This kind of nonlinear analysis is given by the
\emph{weak turbulence theory}, which is the next step in this chain
of perturbative approximations.

Mostly developed in the period between the late $1950$s and early
$1970$s \cite{Kadomtsev1965,Tsytovich1967,saggal,tsynlep,david,
  tsyitotp,akhi2,tsytotp,mel}, the weak turbulence theory has
become a valuable theoretical tool for the analysis of nonlinear
phenomena in plasmas since then, being applied in several studies
until nowadays \cite{Grognard1982,McClements87b,Hanssen1991,
  Edney2001,Kontar2001,Kontar2002,THD13}. Its complex formulation
is constituted by a set of coupled kinetic equations, which describe
the time evolution of the velocity distribution functions of the
plasma particles and the time evolution of the spectral intensities of
the plasma wave modes. The development of the weak turbulence theory
was resumed in a relatively recent series of papers, where the author,
starting from first principles, has extended the original formalism in
order to include new effects. In the initial work, it was considered
only the propagation of electrostatic oscillations, taking into account
the effects of both wave-wave and wave-particle interactions \cite{Yoon00}.
Later, the formalism was expanded, and discrete particle effects,
related to spontaneous emission and spontaneous scattering processes,
were included~\cite{Yoon05a}. In a further extension, the effects of
the propagation of electromagnetic waves were incorporated into the
revised formulation \cite{Yoon06,Yoon2012b}.

@@

The hypothesis about the probable relevance of binary collisions in the
nonlinear dynamics of the beam-plasma interaction was numerically tested
in \cite{Tigik2016a} (see \autoref{master}). In this work, a linearized
form of the Landau collision integral was added to the particle kinetic
equation, and the weak turbulence theory's complete set of self-consistent,
electrostatic equations was numerically integrated in two-dimensions.
It was shown that collisions indeed do affect the plasma dynamics in a
time-scale that is very close to the time-scale of action of nonlinear
effects. Beyond the purely theoretical conjecture, combining collective
processes and collisional effects have some important applications in
solar physics. In the solar hard X-ray emission analysis, for instance, the
models used for interpreting the spectra measured by the Reuven Ramaty High
Energy Solar Spectroscopic Imager (RHESSI)\footnote{For more information
 about the mission see: \url{https://hesperia.gsfc.nasa.gov/rhessi3/}.}
that employ quasilinear/nonlinear wave instabilities with some kind of
collisional dissipation (collisional damping for the waves, binary
collisions for the particles) are usually empirically adapted merely by
adding an \emph{ad hoc} expression into the particles and wave kinetic
equations to fit the observed data \cite{PK95,Kohl1998,Veronig05,Brown2006,
  Kontar2011,KKDSSK11}. However, there is no rigorous theory to compare
and support such models. Moreover, though the formalism in \cite{Tigik2016a}
makes use of the full Landau collision integral in the particle kinetic
equation, it does not take into account collisional damping effects in the
wave equation, which is widely used in these empirical models. The point
is: until that moment, there was not a proper theoretical tool to deal
with the combination of collective processes and collisional interaction.

@@

The theory developed during this graduate research analyses the combined
action of nonlinear kinetic instabilities and collisional processes in
the context of solar physics. To contextualize our work within the solar
plasma research, in Subsections~\ref{solar-physics},~\ref{sun} and
\ref{solar-corona} we present a brief review of the current research in
solar and space physics and the phenomena related to this work. The
corresponding paper is pointed in a footnote.

\subsection{Solar and space physics}
\label{solar-physics}
The domain of solar and space physics is the \emph{heliosphere}, a cavity
in the interstellar medium, created by the constant supersonic flow of solar
plasma that permeates the interplanetary space. This region encloses the
solar system and extends for approximately $140\unit{AU}$\footnote{An AU
  (astronomical unit) is defined as the mean distance between the Sun and
  Earth, $1\unit{AU}\approx 150\times 10^6\unit{km}$.} in the surrounding
galactic space. Its outer limit is the \emph{heliopause}, an interface
zone where the outgoing pressure of the solar plasma balances the incoming
pressure from the interstellar medium. This comet-shaped plasma bubble
\cite{Dialynas2017}, also has an inner boundary, the \emph{termination shock},
which delimits the sphere of absolute influence of the solar plasma. Beyond
the termination shock, at roughly $100\unit{AU}$ from the Sun, extending
out to the heliopause, lies the \emph{heliosheath}. In this region, the
solar wind particles start being subjected to increasing external pressure,
transitioning to a subsonic, turbulent flow that blends and interacts
directly with the matter in the local interstellar medium \cite{NAP13060}.
In \autoref{figE1}, we have a depiction of the regions and boundaries
described above, and the current location of both Voyager missions, that
are already outside the heliosphere, in the interstellar space.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.892\textwidth]{solar_system_env.png}
    \caption{Main boundaries of the heliosphere and the location of both
      Voyager missions.}
      {\footnotesize Credit:}
      \href{https://voyager.jpl.nasa.gov/news/details.php?article_id=112}
      {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
    \label{figE1}
  \end{center}
\end{figure}

The ultimate goal of heliophysics can be summarized as the search for a
better understanding of the solar dynamics and how it affects the Earth,
other planetary bodies, and the interstellar medium. The heliosphere is
a coupled system, where different interacting elements that might look
unrelated at first sight are connected by underlying plasma processes
\cite{NAP13060}. A great example of this interconnection is the relation
between the appearing of sunspots and the occurrence of non-recurrent
geomagnetic storms, which are the most intense space weather disturbances.
Evidence of such relationship started to appear at the end of the $19$th
century. However, the correct hypothesis supporting this correlation
(coronal mass ejections associated with solar flares), which depended
on advances in plasma physics theory, came along only in $1929$
\cite{chapman1929cosmical,Koskinen2011}.

\subsection{The Sun and the near-Earth environment}
\label{sun}
A better comprehension of the Sun and the dynamic space around our planet
goes beyond the pure scientific curiosity. This accessible space physics
laboratory can indeed lead to discoveries that can be applied and extended
to remote cosmic systems. However, the primary reason behind the international
effort (see Figures \ref{nasa} and
\ref{esa}) on understanding the complex physics of the Sun and interplanetary
space is to unlock means of predicting the occurrence and intensity of solar
activity, and anticipate how the near-Earth environment will be affected.
Reliable forecasting of the space weather is essential for protecting
electronic equipment, radio communications, GPS signal and humans in space
from the effects of the interaction between the dense, magnetized plasma of
coronal mass ejections with the geomagnetic field, and also from the
energetic radiation emitted by solar flares\footnote{The emission of hard X-rays
  and type III radio bursts, both generated during solar flares, are addressed in
  \cite{Tigik2016a} (see \autoref{master}).}. Extreme coronal mass ejections
can also cause stronger geomagnetic disturbances that may affect terrestrial
infrastructure such as electric power grids \cite{NAP13060}.
\begin{figure}[hb]
  \begin{center}
    \includegraphics[width=0.892\textwidth]{hso_fleet_chart_april_2019.pdf}
    \caption{NASA's present and future heliophysics system observatory. The number
      between parenthesis under the probe's name is the total number of spacecrafts
      that compose the mission.}
      {\footnotesize Credit:}
      \href{https://science.nasa.gov/heliophysics}
      {\footnotesize NASA}{\footnotesize , accessed at 10/08/2019.}
    \label{nasa}
  \end{center}
\end{figure}
\begin{figure}[ht]
  \begin{center}
    \includegraphics[width=0.892\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
    \caption{ESA's past, present, and future science missions for studying the solar system.}
      {\footnotesize Credit:}
      \href{https://www.esa.int/spaceinimages/Images/2019/02/ESA_s_fleet_of_Solar_System_explorers}
      {\footnotesize ESA}{\footnotesize , accessed at 10/08/2019.}
    \label{esa}
  \end{center}
\end{figure}

\subsection{The solar corona}
\label{solar-corona}
The source of the tenuous magnetized plasma permeating the heliosphere, and
also the origin of solar particles and radiation that may cause disruptive
space weather around Earth, is the outermost layer of the Sun: the solar
corona \cite{Cranmer2017,Klein2017}. The solar corona can be easily recognized
as the bright halo that appears around the hidden Sun during solar eclipses.
\autoref{corona} shows two beautiful photographs of the corona, taken in two
different solar eclipses, August 21 $2017$ and July 2 $2019$. In both pictures,
one can see the moon covering the bright photosphere, allowing us to have a
glimpse of the thin, but ultra-hot coronal plasma.

@@

The main subject of this thesis is discussed in \Cref{noneigenmode}. In
\Cref{sec:inc-non} we show the methodology used in the formulation of this
new generalization and the outcome of its inclusion in the quasilinear
wave equation, and in the particle kinetic equation. \Cref{sec:non-non}
describes the inclusion of the noneigenmode fluctuations in the nonlinear
wave equations and the resulting terms, which are the main concern of
the present analysis. In \Cref{main}, we contextualize the present work
regarding the theory discussed in the previous chapter and present the
results obtained in appended papers. \Cref{cha:final}, summarizes the
results and discuss some remarking conclusions obtained in this analysis.
At the end of this chapter, we also elaborate on the perspectives for this
new generalized formalism and its relevance for the next generation of
solar physics research.
% LFZ190822: Suponho que aqui devia ser "... a brief discussion on the
% conclusions obtained and on the perspectives ..." ?
% Sabrina: Melhorou?
% and its relevance for the next generation of solar physics research are
% also deliberated.

In the end, we have four appendices. \Cref{appA} depicts an improved
approximation for the second order susceptibility of the electrostatic
bremsstrahlung for Langmuir waves. In \Cref{appB} we discuss the
similarities of the asymptotic equilibrium state of the Langmuir waves
spectrum, considering a combination of an inverse power-law kappa
distribution and a Maxwellian distribution, in the presence and the
absence of the electrostatic bremsstrahlung effect. The discussion in
\Cref{appB} is related to the article appended in \Cref{appC}, which
is parallel research and is only slightly connected to the main subject
of this work. \Cref{master} shows the paper that summarizes the results
of my Master’s dissertation, which may be considered the starting point
of this doctoral research. % \Cref{appE} explores relevant aspects of
% current solar physics research and how they are connected to this work.
% It was written to be more like a light, informative reading, than a
% deep academic digression.

@@

Like in the case of non-ionized gases, the statistical description of the
plasma dynamics is given by the Boltzmann equation
\begin{equation}
\frac{\partial f_\alpha({\bf r},{\bf v},t)}{\partial t}
+{\bf v \cdot \nabla_r}f_\alpha({\bf r},{\bf v},t)
 +\frac{{\bf F}}{m_\alpha} {\bf\cdot \nabla_v}f_\alpha({\bf r},{\bf v},t)
=\left(\frac{\partial f_\alpha ({\bf r},{\bf v},t)}{\partial t}\right)_{\rm coll}.
\label{boltz}
\end{equation}

@@

Collisional interactions are the central point of the present thesis. However,
the formalism presented in \Cref{noneigenmode}, departs from the weak turbulence
equations, which are the kinetic description of nonlinear, low-amplitude
instabilities in a collisionless plasma. The contributions of the correlations
between \emph{source} fluctuations, which account for collisional interactions
(see.~\cite{klimon,Tigik2015}), are then retrieved with the inclusion of
noneigenmode contributions in the wave and particle kinetic equations\footnote{
  For instance, in \Cref{sec:inc-non}, it will be shown that including the
  noneigenmode fluctuations in the weak turbulence's formal particle kinetic
  equation leads to an expression that accounts for the collisional interactions
  that appear on the right-hand side of equation~\eqref{boltz}.}. Therefore,
at this point, it will be assumed that collisions can be neglected.

@@

In the general case, the acting force in Eqs. \eqref{boltz} and \eqref{eq:vlasov}
is given by the Lorentz force added by an external force, which, at kinetic scales,
is also of electromagnetic nature. Therefore, in \emph{cgs} units\footnote{The
  use of cgs units will be consistent through all this work.}, ${\bf F}$ has the
following form
\begin{equation}
  {\bf F}=\sum_{\alpha}q_{\alpha}\left[{\bf E}({\bf r},t)
    +\frac{1}{c}{\bf v \times B}({\bf r},t)\right]
  +{\bf F_{ext}},
  \label{florentz}
\end{equation}
where $q_{\alpha}$ is the charge of the particles of kind $\alpha$, and $c$ is
the speed of light. The quantities ${\bf E}({\bf r},t)$ and ${\bf B}({\bf r},t)$
are, respectively, the electric and magnetic fields, which are described by the
Maxwell equations
\begin{eqnarray}
  \label{max1}
  {\bf \nabla \cdot E}&=& 4\pi\rho\\
  \label{max2}
  {\bf \nabla \cdot B}&=& 0\\
  \label{max3}
    {\bf \nabla \times E}&=& -\frac{1}{c}
   \frac{\partial {\bf B}}{\partial t}\\
  \label{max4}
    {\bf \nabla \times B}&=& \frac{4\pi}{c}{\bf J}
    +\frac{1}{c}\frac{\partial{\bf E}}{\partial t}.
\end{eqnarray}

@@

\chapter{Weak turbulence theory}
\label{cha:weak-turb}
The weak turbulence theory is what we may call a ``borderline approach''
because, despite the fact that it deals with some more intense
instabilities, we must assure that these fluctuations are still inside
the weak turbulence limit, i.e., that the turbulence is weak enough to be
treated by a perturbative method. Such boundary is defined by a comparison
between the averaged kinetic energy of the particles per volume unity
${\cal E}_{kin}=\bar n m<v^2>/2$, and the energy density ${\cal E}_f$, which
is associated with the fluctuations of the perturbative electric field.
Thus, by ``weak turbulence'' we mean
\begin{equation}
  \label{eq:weak}
  {\cal E}_f \ll {\cal E}_{kin},
\end{equation}
that is,
% LFZ180216: Não fica melhor com vírgula depois de "that is"?
% Sabrina: OK
the energy density of the fluctuations must be much smaller
% LFZ180216: Ou simplesmente "much smaller"?
% Sabrina: OK
than the kinetic energy density of the particles. This condition is
related to the slow wave-growing assumption \cite{david}, which is
central for the further development of nonlinear kinetic equations,
as will be discussed further.

@@

\section{Nonlinear kinetic equations}
\label{sec:kin-gen-eq}
Let us consider the propagation of electrostatic oscillations
in a homogeneous, unmagnetized and fully ionized plasma. Thus,
in the absence of collisions, the movement equation is given
by the electrostatic Vlasov equation
\begin{equation}
  \label{vlasov-nl}
  \frac{\partial f_a({\bf r}, {\bf v},t)}{\partial t}
+{\bf v \cdot \nabla}f_a({\bf r}, {\bf v},t)
+\frac{e_a}{m_a}{\bf E}({\bf r},t){\bf \cdot}
\frac{\partial f_a({\bf r},{\bf v},t)}{\partial \bf v}=0,
\end{equation}
where the electric field is given by
\begin{equation}
   {\bf \nabla \cdot E}({\bf r},t)
   =4\pi \hat n \sum_a e_a\int d^3 v f_a({\bf r}, {\bf v},t). 
\end{equation}
In the above equations, $f_a$ is the velocity distribution function,
where the subscript ``$a$'' is the kind of particle: $a=i$ for ions
and $a=e$ for electrons. For an overall neutral plasma, the average
number density of
% LFZ180216: Sugestão "the number density of"
% Sabrina: OK
the ions and the electrons is the same, $\hat n = \hat n_e = \hat n_i$.
